### 2015-09-15 Projects/DelCo_2012/Report/DelCo_2012.tex
edit files Delco2012

@@

\subsection{Furniture Fuel Package}
\label{subsec:Furniture_Fuel_Package}

Figures~\ref{fig:Test_1_First_Suppression} and \ref{fig:Test_1_Second_Suppression} provide and overview of the impact of 30$^{\circ}$ fog CAF application after 15~s of application from the hallway nozzle and then 15~s of application from the room nozzle. The figures provide change in temperature and heat flux at several positions and elevations through the structure. These values are taken immediately before and after application to assess the application agent, stream, and location on interior conditions.

@@

@@

@@

% \chapter{Appendix}
% \label{chap:Appendix}

% \section{Test 1 Figures}
% \label{subsec:Test_1_Figures}

% \subsection{Temperature}
% \label{subsec:Temperature}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/FSE1_Eastside_Array}
% 	\caption{Test 1 (FSE1): Eastside Array}
% 	\label{fig:Test_1_Eastside_Array}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/FSE1_Westside_Array}
% 	\caption{Test 1 (FSE1): Westside Array}
% 	\label{fig:Test_1_Westside_Array}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/FSE1_Hallway_Array}
% 	\caption{Test 1 (FSE1): Hallway Array}
% 	\label{fig:Test_1_Hallway_Array}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/FSE1_Doorway_Array}
% 	\caption{Test 1 (FSE1): Doorway Array}
% 	\label{fig:Test_1_Doorway_Array}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE1_Eastside_Array}
% 	\caption{Test 1 (FSE1): Suppression Eastside Array}
% 	\label{fig:Test_1_Suppression_Eastside_Array}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE1_Westside_Array}
% 	\caption{Test 1 (FSE1): Suppression Westside Array}
% 	\label{fig:Test_1_Suppression_Westside_Array}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE1_Hallway_Array}
% 	\caption{Test 1 (FSE1): Suppression Hallway Array}
% 	\label{fig:Test_1_Suppression_Hallway_Array}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE1_Doorway_Array}
% 	\caption{Test 1 (FSE1): Suppression Doorway Array}
% 	\label{fig:Test_1_Suppression_Doorway_Array}
% \end{figure}

% \subsection{Heat Flux}
% \label{subsec:Heat_Flux}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_1_Heat_Flux_Eastside}
% 	\caption{Test 1 (FSE1): Eastside Heat Flux}
% 	\label{fig:Test_1_Eastside_Heat_Flux}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_1_Heat_Flux_Westside}
% 	\caption{Test 1 (FSE1): Westside Heat Flux}
% 	\label{fig:Test_1_Westside_Heat_Flux}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_1_Heat_Flux_Hallway}
% 	\caption{Test 1 (FSE1): Hallway Heat Flux}
% 	\label{fig:Test_1_Hallway_Heat_Flux}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_1_Heat_Flux_Near_Fire_Room}
% 	\caption{Test 1 (FSE1): Heat Flux Near Fire Room}
% 	\label{fig:Test_1_Heat_Flux_Near_Fire_Room}
% \end{figure}

% \subsection{Velocity}
% \label{subsec:Velocity}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Velocity/FSE_Test_1_Hallway_Velocity}
% 	\caption{Test 1 (FSE1): Hallway Velocity}
% 	\label{fig:Test_1_Hallway_Velocity}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Velocity/FSE_Test_1_Doorway_Velocity}
% 	\caption{Test 1 (FSE1): Doorway Velocity}
% 	\label{fig:Test_1_Doorway_Velocity}
% \end{figure}

% \clearpage

% \section{Test 2 Figures}
% \label{subsec:Test_2_Figures}

% \subsection{Temperature}
% \label{subsec:Temperature}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/FSW2_Eastside_Array}
% 	\caption{Test 2 (FSW2): Eastside Array}
% 	\label{fig:Test_2_Eastside_Array}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/FSW2_Westside_Array}
% 	\caption{Test 2 (FSW2: Westside Array}
% 	\label{fig:Test_2_Westside_Array}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/FSW2_Hallway_Array}
% 	\caption{Test 2 (FSW2): Hallway Array}
% 	\label{fig:Test_2_Hallway_Array}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/FSW2_Doorway_Array}
% 	\caption{Test 2 (FSW2): Doorway Array}
% 	\label{fig:Test_2_Doorway_Array}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW2_Eastside_Array}
% 	\caption{Test 2 (FSW2): Suppression Eastside Array}
% 	\label{fig:Test_2_Suppression_Eastside_Array}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW2_Westside_Array}
% 	\caption{Test 2 (FSW2): Suppression Westside Array}
% 	\label{fig:Test_2_Suppression_Westside_Array}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW2_Hallway_Array}
% 	\caption{Test 2 (FSW2): Suppression Hallway Array}
% 	\label{fig:Test_2_Suppression_Hallway_Array}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW2_Doorway_Array}
% 	\caption{Test 2 (FSW2): Suppression Doorway Array}
% 	\label{fig:Test_2_Suppression_Doorway_Array}
% \end{figure}

% \subsection{Heat Flux}
% \label{subsec:Heat_Flux}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_2_Heat_Flux_Eastside}
% 	\caption{Test 2 (FSW2): Eastside Heat Flux}
% 	\label{fig:Test_2_Eastside_Heat_Flux}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_2_Heat_Flux_Westside}
% 	\caption{Test 2 (FSW2): Westside Heat Flux}
% 	\label{fig:Test_2_Westside_Heat_Flux}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_2_Heat_Flux_Hallway}
% 	\caption{Test 2 (FSW2): Hallway Heat Flux}
% 	\label{fig:Test_2_Hallway_Heat_Flux}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_2_Heat_Flux_Near_Fire_Room}
% 	\caption{Test 2 (FSW2): Heat Flux Near Fire Room}
% 	\label{fig:Test_2_Heat_Flux_Near_Fire_Room}
% \end{figure}

% \subsection{Velocity}
% \label{subsec:Velocity}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Velocity/FSW_Test_2_Hallway_Velocity}
% 	\caption{Test 2 (FSW2): Hallway Velocity}
% 	\label{fig:Test_2_Hallway_Velocity}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Velocity/FSW_Test_2_Doorway_Velocity}
% 	\caption{Test 2 (FSW2): Doorway Velocity}
% 	\label{fig:Test_2_Doorway_Velocity}
% \end{figure}

% \clearpage

% \section{Test 3 Figures}
% \label{subsec:Test_3_Figures}

% \subsection{Temperature}
% \label{subsec:Temperature}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/FSW3_Eastside_Array}
% 	\caption{Test 3 (FSW3): Eastside Array}
% 	\label{fig:Test_3_Eastside_Array}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/FSW3_Westside_Array}
% 	\caption{Test 3 (FSW3: Westside Array}
% 	\label{fig:Test_3_Westside_Array}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/FSW3_Hallway_Array}
% 	\caption{Test 3 (FSW3): Hallway Array}
% 	\label{fig:Test_3_Hallway_Array}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/FSW3_Doorway_Array}
% 	\caption{Test 3 (FSW3): Doorway Array}
% 	\label{fig:Test_3_Doorway_Array}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW3_Eastside_Array}
% 	\caption{Test 3 (FSW3): Suppression Eastside Array}
% 	\label{fig:Test_3_Suppression_Eastside_Array}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW3_Westside_Array}
% 	\caption{Test 3 (FSW3): Suppression Westside Array}
% 	\label{fig:Test_3_Suppression_Westside_Array}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW3_Hallway_Array}
% 	\caption{Test 3 (FSW3): Suppression Hallway Array}
% 	\label{fig:Test_3_Suppression_Hallway_Array}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW3_Doorway_Array}
% 	\caption{Test 3 (FSW3): Suppression Doorway Array}
% 	\label{fig:Test_3_Suppression_Doorway_Array}
% \end{figure}

% \subsection{Heat Flux}
% \label{subsec:Heat_Flux}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_3_Heat_Flux_Eastside}
% 	\caption{Test 3 (FSW3): Eastside Heat Flux}
% 	\label{fig:Test_3_Eastside_Heat_Flux}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_3_Heat_Flux_Westside}
% 	\caption{Test 3 (FSW3): Westside Heat Flux}
% 	\label{fig:Test_3_Westside_Heat_Flux}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_3_Heat_Flux_Hallway}
% 	\caption{Test 3 (FSW3): Hallway Heat Flux}
% 	\label{fig:Test_3_Hallway_Heat_Flux}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_3_Heat_Flux_Near_Fire_Room}
% 	\caption{Test 3 (FSW3): Heat Flux Near Fire Room}
% 	\label{fig:Test_3_Heat_Flux_Near_Fire_Room}
% \end{figure}

% \subsection{Velocity}
% \label{subsec:Velocity}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Velocity/FSW_Test_3_Hallway_Velocity}
% 	\caption{Test 3 (FSW3): Hallway Velocity}
% 	\label{fig:Test_3_Hallway_Velocity}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Velocity/FSW_Test_3_Doorway_Velocity}
% 	\caption{Test 3 (FSW3): Doorway Velocity}
% 	\label{fig:Test_3_Doorway_Velocity}
% \end{figure}

% \clearpage

% \section{Test 4 Figures}
% \label{subsec:Test_4_Figures}

% \subsection{Temperature}
% \label{subsec:Temperature}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/FSE4_Eastside_Array}
% 	\caption{Test 4 (FSE4): Eastside Array}
% 	\label{fig:Test_4_Eastside_Array}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/FSE4_Westside_Array}
% 	\caption{Test 4 (FSE4): Westside Array}
% 	\label{fig:Test_4_Westside_Array}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/FSE4_Hallway_Array}
% 	\caption{Test 4 (FSE4): Hallway Array}
% 	\label{fig:Test_4_Hallway_Array}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/FSE4_Doorway_Array}
% 	\caption{Test 4 (FSE4): Doorway Array}
% 	\label{fig:Test_4_Doorway_Array}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE4_Eastside_Array}
% 	\caption{Test 4 (FSE4): Suppression Eastside Array}
% 	\label{fig:Test_4_Suppression_Eastside_Array}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE4_Westside_Array}
% 	\caption{Test 4 (FSE4): Suppression Westside Array}
% 	\label{fig:Test_4_Suppression_Westside_Array}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE4_Hallway_Array}
% 	\caption{Test 4 (FSE4): Suppression Hallway Array}
% 	\label{fig:Test_4_Suppression_Hallway_Array}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE4_Doorway_Array}
% 	\caption{Test 4 (FSE4): Suppression Doorway Array}
% 	\label{fig:Test_4_Suppression_Doorway_Array}
% \end{figure}

% \subsection{Heat Flux}
% \label{subsec:Heat_Flux}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_4_Heat_Flux_Eastside}
% 	\caption{Test 4 (FSE4): Eastside Heat Flux}
% 	\label{fig:Test_4_Eastside_Heat_Flux}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_4_Heat_Flux_Westside}
% 	\caption{Test 4 (FSE4): Westside Heat Flux}
% 	\label{fig:Test_4_Westside_Heat_Flux}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_4_Heat_Flux_Hallway}
% 	\caption{Test 4 (FSE4): Hallway Heat Flux}
% 	\label{fig:Test_4_Hallway_Heat_Flux}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_4_Heat_Flux_Near_Fire_Room}
% 	\caption{Test 4 (FSE4): Heat Flux Near Fire Room}
% 	\label{fig:Test_4_Heat_Flux_Near_Fire_Room}
% \end{figure}

% \subsection{Velocity}
% \label{subsec:Velocity}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Velocity/FSE_Test_4_Hallway_Velocity}
% 	\caption{Test 4 (FSE4): Hallway Velocity}
% 	\label{fig:Test_4_Hallway_Velocity}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Velocity/FSE_Test_4_Doorway_Velocity}
% 	\caption{Test 4 (FSE4): Doorway Velocity}
% 	\label{fig:Test_4_Doorway_Velocity}
% \end{figure}

% \clearpage

% \section{Test 5 Figures}
% \label{subsec:Test_5_Figures}

% \subsection{Temperature}
% \label{subsec:Temperature}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/FSE5_Eastside_Array}
% 	\caption{Test 5 (FSE5): Eastside Array}
% 	\label{fig:Test_5_Eastside_Array}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/FSE5_Westside_Array}
% 	\caption{Test 5 (FSE5): Westside Array}
% 	\label{fig:Test_5_Westside_Array}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/FSE5_Hallway_Array}
% 	\caption{Test 5 (FSE5): Hallway Array}
% 	\label{fig:Test_5_Hallway_Array}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/FSE5_Doorway_Array}
% 	\caption{Test 5 (FSE5): Doorway Array}
% 	\label{fig:Test_5_Doorway_Array}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE5_Eastside_Array}
% 	\caption{Test 5 (FSE5): Suppression Eastside Array}
% 	\label{fig:Test_5_Suppression_Eastside_Array}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE5_Westside_Array}
% 	\caption{Test 5 (FSE5): Suppression Westside Array}
% 	\label{fig:Test_5_Suppression_Westside_Array}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE5_Hallway_Array}
% 	\caption{Test 5 (FSE5): Suppression Hallway Array}
% 	\label{fig:Test_5_Suppression_Hallway_Array}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE5_Doorway_Array}
% 	\caption{Test 5 (FSE5): Suppression Doorway Array}
% 	\label{fig:Test_5_Suppression_Doorway_Array}
% \end{figure}

% \subsection{Heat Flux}
% \label{subsec:Heat_Flux}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_5_Heat_Flux_Eastside}
% 	\caption{Test 5 (FSE5): Eastside Heat Flux}
% 	\label{fig:Test_5_Eastside_Heat_Flux}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_5_Heat_Flux_Westside}
% 	\caption{Test 5 (FSE5): Westside Heat Flux}
% 	\label{fig:Test_5_Westside_Heat_Flux}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_5_Heat_Flux_Hallway}
% 	\caption{Test 5 (FSE5): Hallway Heat Flux}
% 	\label{fig:Test_5_Hallway_Heat_Flux}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_5_Heat_Flux_Near_Fire_Room}
% 	\caption{Test 5 (FSE5): Heat Flux Near Fire Room}
% 	\label{fig:Test_5_Heat_Flux_Near_Fire_Room}
% \end{figure}

% \subsection{Velocity}
% \label{subsec:Velocity}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Velocity/FSE_Test_5_Hallway_Velocity}
% 	\caption{Test 5 (FSE5): Hallway Velocity}
% 	\label{fig:Test_5_Hallway_Velocity}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Velocity/FSE_Test_5_Doorway_Velocity}
% 	\caption{Test 5 (FSE5): Doorway Velocity}
% 	\label{fig:Test_5_Doorway_Velocity}
% \end{figure}

% \clearpage

% \section{Test 6 Figures}
% \label{subsec:Test_6_Figures}

% \subsection{Temperature}
% \label{subsec:Temperature}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/FSW6_Eastside_Array}
% 	\caption{Test 6 (FSW6): Eastside Array}
% 	\label{fig:Test_6_Eastside_Array}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/FSW6_Westside_Array}
% 	\caption{Test 6 (FSW6: Westside Array}
% 	\label{fig:Test_6_Westside_Array}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/FSW6_Hallway_Array}
% 	\caption{Test 6 (FSW6): Hallway Array}
% 	\label{fig:Test_6_Hallway_Array}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/FSW6_Doorway_Array}
% 	\caption{Test 6 (FSW6): Doorway Array}
% 	\label{fig:Test_6_Doorway_Array}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW6_Eastside_Array}
% 	\caption{Test 6 (FSW6): Suppression Eastside Array}
% 	\label{fig:Test_6_Suppression_Eastside_Array}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW6_Westside_Array}
% 	\caption{Test 6 (FSW6): Suppression Westside Array}
% 	\label{fig:Test_6_Suppression_Westside_Array}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW6_Hallway_Array}
% 	\caption{Test 6 (FSW6): Suppression Hallway Array}
% 	\label{fig:Test_6_Suppression_Hallway_Array}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW6_Doorway_Array}
% 	\caption{Test 6 (FSW6): Suppression Doorway Array}
% 	\label{fig:Test_6_Suppression_Doorway_Array}
% \end{figure}

% \subsection{Heat Flux}
% \label{subsec:Heat_Flux}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_6_Heat_Flux_Eastside}
% 	\caption{Test 6 (FSW6): Eastside Heat Flux}
% 	\label{fig:Test_6_Eastside_Heat_Flux}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_6_Heat_Flux_Westside}
% 	\caption{Test 6 (FSW6): Westside Heat Flux}
% 	\label{fig:Test_6_Westside_Heat_Flux}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_6_Heat_Flux_Hallway}
% 	\caption{Test 6 (FSW6): Hallway Heat Flux}
% 	\label{fig:Test_6_Hallway_Heat_Flux}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_6_Heat_Flux_Near_Fire_Room}
% 	\caption{Test 6 (FSW6): Heat Flux Near Fire Room}
% 	\label{fig:Test_6_Heat_Flux_Near_Fire_Room}
% \end{figure}

% \subsection{Velocity}
% \label{subsec:Velocity}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Velocity/FSW_Test_6_Hallway_Velocity}
% 	\caption{Test 6 (FSW6): Hallway Velocity}
% 	\label{fig:Test_6_Hallway_Velocity}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Velocity/FSW_Test_6_Doorway_Velocity}
% 	\caption{Test 6 (FSW6): Doorway Velocity}
% 	\label{fig:Test_6_Doorway_Velocity}
% \end{figure}

% \clearpage

% \section{Test 7 Figures}
% \label{subsec:Test_7_Figures}

% \subsection{Temperature}
% \label{subsec:Temperature}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/FSW7_Eastside_Array}
% 	\caption{Test 7 (FSW7): Eastside Array}
% 	\label{fig:Test_7_Eastside_Array}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/FSW7_Westside_Array}
% 	\caption{Test 7 (FSW7: Westside Array}
% 	\label{fig:Test_7_Westside_Array}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/FSW7_Hallway_Array}
% 	\caption{Test 7 (FSW7): Hallway Array}
% 	\label{fig:Test_7_Hallway_Array}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/FSW7_Doorway_Array}
% 	\caption{Test 7 (FSW7): Doorway Array}
% 	\label{fig:Test_7_Doorway_Array}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW7_Eastside_Array}
% 	\caption{Test 7 (FSW7): Suppression Eastside Array}
% 	\label{fig:Test_7_Suppression_Eastside_Array}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW7_Westside_Array}
% 	\caption{Test 7 (FSW7): Suppression Westside Array}
% 	\label{fig:Test_7_Suppression_Westside_Array}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW7_Hallway_Array}
% 	\caption{Test 7 (FSW7): Suppression Hallway Array}
% 	\label{fig:Test_7_Suppression_Hallway_Array}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW7_Doorway_Array}
% 	\caption{Test 7 (FSW7): Suppression Doorway Array}
% 	\label{fig:Test_7_Suppression_Doorway_Array}
% \end{figure}

% \subsection{Heat Flux}
% \label{subsec:Heat_Flux}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_7_Heat_Flux_Eastside}
% 	\caption{Test 7 (FSW7): Eastside Heat Flux}
% 	\label{fig:Test_7_Eastside_Heat_Flux}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_7_Heat_Flux_Westside}
% 	\caption{Test 7 (FSW7): Westside Heat Flux}
% 	\label{fig:Test_7_Westside_Heat_Flux}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_7_Heat_Flux_Hallway}
% 	\caption{Test 7 (FSW7): Hallway Heat Flux}
% 	\label{fig:Test_7_Hallway_Heat_Flux}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_7_Heat_Flux_Near_Fire_Room}
% 	\caption{Test 7 (FSW7): Heat Flux Near Fire Room}
% 	\label{fig:Test_7_Heat_Flux_Near_Fire_Room}
% \end{figure}

% \subsection{Velocity}
% \label{subsec:Velocity}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Velocity/FSW_Test_7_Hallway_Velocity}
% 	\caption{Test 7 (FSW7): Hallway Velocity}
% 	\label{fig:Test_7_Hallway_Velocity}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Velocity/FSW_Test_7_Doorway_Velocity}
% 	\caption{Test 7 (FSW7): Doorway Velocity}
% 	\label{fig:Test_7_Doorway_Velocity}
% \end{figure}

% \clearpage

% \section{Test 8 Figures}
% \label{subsec:Test_8_Figures}

% \subsection{Temperature}
% \label{subsec:Temperature}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/FSE8_Eastside_Array}
% 	\caption{Test 8 (FSE8): Eastside Array}
% 	\label{fig:Test_8_Eastside_Array}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/FSE8_Westside_Array}
% 	\caption{Test 8 (FSE8): Westside Array}
% 	\label{fig:Test_8_Westside_Array}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/FSE8_Hallway_Array}
% 	\caption{Test 8 (FSE8): Hallway Array}
% 	\label{fig:Test_8_Hallway_Array}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/FSE8_Doorway_Array}
% 	\caption{Test 8 (FSE8): Doorway Array}
% 	\label{fig:Test_8_Doorway_Array}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE8_Eastside_Array}
% 	\caption{Test 8 (FSE8): Suppression Eastside Array}
% 	\label{fig:Test_8_Suppression_Eastside_Array}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE8_Westside_Array}
% 	\caption{Test 8 (FSE8): Suppression Westside Array}
% 	\label{fig:Test_8_Suppression_Westside_Array}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE8_Hallway_Array}
% 	\caption{Test 8 (FSE8): Suppression Hallway Array}
% 	\label{fig:Test_8_Suppression_Hallway_Array}
% \end{figure}

>>>>

The 88 gas cooling experiments were completed as part of 9 separate tests in the burn building. During each test, the fire was ignited and the fire developed until the temperature 1.83~m (6~ft) below the ceiling in the gas cooling room reached or exceeded 260~$^{\circ}$C (500~$^{\circ}$F). Once this criteria was met, gas cooling began.

\begin{figure}[!ht]
	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/7_8_Solid_mid_scatter}
	\caption{CAFS vs Water Gas Cooling Comparison for 7/8 Solid Stream}
	\label{fig:CAFS_Water_Comp_7_8}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/SS_mid_scatter}
	\caption{CAFS vs Water Gas Cooling Comparison for Straight Stream Mid Position}
	\label{fig:CAFS_Water_Comp_SS_mid}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/SS_full_back_scatter}
	\caption{CAFS vs Water Gas Cooling Comparison for Straight Stream Full Back Position}
	\label{fig:CAFS_Water_Comp_SS_full}
\end{figure}

@@

Figures~\ref{fig:Test_1_First_Suppression} and \ref{fig:Test_1_Second_Suppression} provide and overview of the impact of 30$^{\circ}$ fog CAF application on the furniture fuel package after 15~s of application from the hallway nozzle and then 15~s of application from the room nozzle (FSE1 in Table~\ref{tab:Test_Descriptions}). The figures provide change in temperature and heat flux measurements at several positions and elevations through the structure: structure doorway, hallway, and three locations within the burn room. These values are taken immediately before and after application to assess the application agent, stream, and location on interior conditions.

@@

The same fuel load, ventilation, and suppression application durations were also tested with water as the suppression agent (FSW2 in Table~\ref{tab:Test_Descriptions}). Figures~\ref{fig:Test_2_First_Suppression} and \ref{fig:Test_2_Second_Suppression} show the results from these tests.

@@

Note that while there are some differences in the changes in temperature and heat flux when comparing CAFs to Water, differences are not substantial. Both suppression agents had similar, significant impact in reducing the high-temperature, high-heat flux environment that existed before suppression. The remainder of these fire suppression images for both the furniture and wood pallet fuel loads can be found in Appendix~\ref{app:fire_suppression}.

@@
